\vskip-0.6in LOBBYING AND LEGISLATIVE UNCERTAINTY

### 2016-02-24 draft.tex
clarify players, strategy spaces and timing in sec:model

The model is based on Banks' (2000) model of vote buying in a legislature, which is in turn a discrete version of Groseclose and Snyder's (1996) model with a continuum of legislators. The major difference here is the addition of uncertainty about the legislator's ideal points.

Each of three legislators faces a choice between the status quo, $x$ and a new policy proposal $s$. The utility function of legislator $i$ is given by $v(i) = u_i(x) - u_i(s)$, which is measured in money units. Note that legislators only have preferences about how they vote, not over which alternative wins.

There are two vote buyers labeled $A$ and $B$ who each prefers to maximize the expected value of his preferred policy net of the bribes he has to pay. $A$ prefers policy $x$ and has willingness to pay (WTP) $W_A$ for $x$ measured in money and values $s$ at zero. $B$ prefers $s$and has WTP $W_B$ for $s$. Each vote buyer would prefer to concede the issue rather than pay more than his WTP.

>>>>

The model borrows much from Banks' (2000) model of vote buying in a legislature, which is in turn a discrete version of Groseclose and Snyder's (1996) model with a continuum of legislators. The major difference here is the addition of uncertainty about the legislators' ideal points.

There are five players in the model. Each of three legislators faces a choice between the status quo, $x$ and a new policy proposal $s$. The utility function of legislator $i$ is given by $v(i) = u_i(x) - u_i(s)$, which is measured in money units. Note that legislators only have preferences about how they vote, not over which alternative wins.

There are two vote buyers labeled $A$ and $B$ who each prefers to maximize the expected value of his preferred policy net of the bribes he has to pay; each chooses a vector of three non-negative bribes. $A$ prefers policy $x$ and has willingness to pay (WTP) $W_A$ for $x$ measured in money and values $s$ at zero. $B$ prefers $s$ and has WTP $W_B$ for $s$ and values $x$ at zero.
